---
title: "Report october 21"
author: "Mireia Triguero"
date: "10/21/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment=NA, warning=FALSE, message=FALSE)
library(wesanderson)
library(tidyverse)
library(xtable)
library(stargazer)
setwd("~/Desktop/Sociology/RA/Data")
staff_salaries <- read_csv("staff_salaries_full.csv") %>%
  mutate(race_member2 = case_when(race_member == 0 ~ "White",
                                  race_member == 1 ~ "Black",
                                  race_member == 2 ~ "Hispanic",
                                  race_member == 3 ~ "Asian",
                                  TRUE ~ NA_character_))
options(qwraps2_markup = "markdown")
race_staffer <- read_csv("race_staffer.csv") %>% dplyr::select(-X1)

multiply100 <- function(x){
  x1 <- x*100
  return(x1)
}
```
## Racial make up for the House:


```{r}

staff_salaries %>% filter(office_type_id =="HM") %>% 
  distinct(core_person_id, .keep_all = TRUE) %>%
  group_by(race) %>% 
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(percentage = round(n/sum(n)*100, 1)) 

```
## Racial make up for Congress:


```{r}

staff_salaries %>% filter(office_type_id =="HM" | office_type_id =="SM") %>% 
  distinct(core_person_id, office_type_id, .keep_all = TRUE) %>%
  group_by(race) %>% 
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(percentage = round(n/sum(n)*100, 1)) 

```

## Revised chart of the racial and gender make up for the House

This is the same one as in the october_6_report_updated pdf. 
```{r}
staff_salaries %>% filter(office_type_id =="HM") %>% 
  filter(!is.na(gender)) %>% group_by(race, gender, core_person_id) %>% 
  summarise(n = n()) %>%
  dplyr::select(-n) %>%
  group_by(race, gender) %>% 
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(percentage = round(n/sum(n)*100,1)) 
```
## Revised chart of the racial and gender make up for Congress:

```{r}
staff_salaries %>% filter(office_type_id =="HM" | office_type_id =="SM") %>% 
  filter(!is.na(gender)) %>% group_by(race, gender, core_person_id) %>% 
  summarise(n = n()) %>%
  dplyr::select(-n) %>%
  group_by(race, gender) %>% 
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(percentage = round(n/sum(n)*100,1)) 
```

## Racial composition of members of Congress in our dataset. Race alone:

```{r}
staff_salaries %>% filter(office_type_id =="HM" | office_type_id =="SM" ) %>% 
  distinct(member_id, .keep_all = TRUE) %>%
  group_by(race_member2) %>% 
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(percentage = round(n/sum(n)*100,1))
````

## and then a chart by race and party: Republicans
```{r }
staff_salaries %>% filter(office_type_id =="HM" | office_type_id =="SM") %>% 
  filter(party_id == 1) %>%
  distinct(member_id, .keep_all = TRUE) %>%
  group_by(race_member2) %>% 
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(percentage = round(n/sum(n)*100,1))
````

## And then a chart by race and party: Democrats
```{r cars}
staff_salaries %>% filter(office_type_id =="HM" | office_type_id =="SM") %>% 
  filter(party_id == 2) %>%
  distinct(member_id, .keep_all = TRUE) %>%
  group_by( race_member2) %>% 
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(percentage = round(n/sum(n)*100,1))
````

## Can I also have a table that illustrates the employment of racial groups by the race of lawmakers.


```{r}
staff_salaries %>% filter(office_type_id =="HM" | office_type_id == "SM") %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(race_member2) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 
```

## Thus can I have a chart for Racial Composition of Congressional Offices According to lawmakers’ Race and Ethnicity: House

```{r}

staff_salaries %>% filter(office_type_id =="HM") %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(race_member2) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 

```

## Thus can i have a chart for Racial Composition of Congressional Offices According to lawmakers’ Race and Ethnicity: Senate

```{r}

staff_salaries %>% filter(office_type_id =="SM") %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(race_member2) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 

```

## a chart  for the racial composition of congressional offices by political party for the House , Senate, and Congress. i.e. What is the racial composition of Democratic offices in the House, Senate, and Overall

```{r}

p1 <- staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
  filter(party_id == 2) %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(office_type_id) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 

p2 <- staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
  filter(party_id == 2) %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) %>%
  mutate(office_type_id = "Congress")

bind_rows(p1,p2)

```

## A chart  for the racial composition of congressional offices by political party for the House , Senate, and Congress. i.e. What is the racial composition of Republican offices in the House, Senate, and Overall

```{r}

p3 <- staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
  filter(party_id == 1) %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(office_type_id) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 

p4 <- staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
  filter(party_id == 1) %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) %>%
  mutate(office_type_id = "Congress")

bind_rows(p3,p4)
```
