---
title: "Report for James"
author: "Mireia Triguero"
date: "10/5/2020"
output:
  pdf_document: default
  html_document: default 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment=NA, warning=FALSE, message=FALSE)
library(wesanderson)
library(tidyverse)
library(xtable)
library(stargazer)
setwd("~/Desktop/Sociology/RA/Data")
staff_salaries <- read_csv("staff_salaries_full.csv") %>%
  mutate(race_member2 = case_when(race_member == 0 ~ "White",
                                  race_member == 1 ~ "Black",
                                  race_member == 2 ~ "Hispanic",
                                  race_member == 3 ~ "Asian",
                                  TRUE ~ NA_character_))
options(qwraps2_markup = "markdown")
race_staffer <- read_csv("race_staffer.csv") %>% dplyr::select(-X1)

multiply100 <- function(x){
  x1 <- x*100
  return(x1)
}
```

##  The racial  and gender make up for the House 
```{r house}

staff_salaries %>% filter(office_type_id =="HM") %>% 
  filter(!is.na(gender)) %>% group_by(race, gender, core_person_id) %>% 
  summarise(n = n()) %>%
  dplyr::select(-n) %>%
  group_by(race, gender) %>% 
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(percentage = round(n/sum(n)*100,1)) 

```
##  The racial and gender make up for the Senate 
```{r senate}

staff_salaries %>% filter(office_type_id =="SM") %>% 
filter(!is.na(gender)) %>% group_by(race, gender, core_person_id) %>% 
  summarise(n = n()) %>%
  dplyr::select(-n) %>%
  group_by(race, gender) %>% 
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(percentage = round(n/sum(n)*100,1))

```

# Office composition by lawmaker’s race and political party in the House and Senate (i.e. White Democrats, White Republicans, Black Democrats, Black Republicans)

## House Democrats
```{r House, democrat, white}


staff_salaries %>% filter(office_type_id =="HM" & party_id == 2) %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(race_member2) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 

```

## House Republicans
```{r House, republicans}

staff_salaries %>% filter(office_type_id =="HM" & party_id == 1) %>% 
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(race_member2) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 


```


## Senate Democrats
```{r senate, democrat}

staff_salaries %>% filter(office_type_id =="SM" & party_id == 2) %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(race_member2) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 


```
## Senate Republicans (No Black Rep. Senators in the data)

```{r senate, republican}

staff_salaries %>% filter(office_type_id =="SM" & party_id == 1) %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(race_member2) %>%
  filter(race_member != 1) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1)


```

## Racial composition of staff Ranking by lawmaker’s race and political party  in the  House and Senate (i.e. White Democrats, White Republicans, Black Democrats, Black Republicans)

## House: White Democrats

```{r}

staff_salaries %>% filter(office_type_id =="HM" & party_id == 2 & race_member == 0) %>%
  distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```
## House: Black Democrats

```{r}

staff_salaries %>% filter(office_type_id =="HM" & party_id == 2 & race_member == 1) %>%
  distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```
## House: Hispanic Democrats

```{r}

staff_salaries %>% filter(office_type_id =="HM" & party_id == 2 & race_member == 2) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## House: Asian Democrats

```{r}

staff_salaries %>% filter(office_type_id =="HM" & party_id == 2 & race_member == 3) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## House: White Republicans

```{r}

staff_salaries %>% filter(office_type_id =="HM" & party_id == 1 & race_member == 0) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```
## House: Black Republicans

```{r}

staff_salaries %>% filter(office_type_id =="HM" & party_id == 1 & race_member == 1) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## House: Hispanic Republicans

```{r}

staff_salaries %>% filter(office_type_id =="HM" & party_id == 1 & race_member == 2) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## House: Asian Republicans

```{r}

staff_salaries %>% filter(office_type_id =="HM" & party_id == 1 & race_member == 3) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## Senate: White Democrats

```{r}

staff_salaries %>% filter(office_type_id =="SM" & party_id == 2 & race_member == 0) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```

## Senate: Black Democrats

```{r}

staff_salaries %>% filter(office_type_id =="SM" & party_id == 2 & race_member == 1) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## Senate: Hispanic Democrats

```{r}

staff_salaries %>% filter(office_type_id =="SM" & party_id == 2 & race_member == 2) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## Senate: Asian Democrats

```{r}

staff_salaries %>% filter(office_type_id =="SM" & party_id == 2 & race_member == 3) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## Senate: White Republicans

```{r}

staff_salaries %>% filter(office_type_id =="SM" & party_id == 1 & race_member == 0) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```
## Senate: Black Republicans (doesn't exist in the data)

## Senate: Hispanic Republicans

```{r}

staff_salaries %>% filter(office_type_id =="SM" & party_id == 1 & race_member == 2) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## Senate: Asian Republicans

```{r}

staff_salaries %>% filter(office_type_id =="SM" & party_id == 1 & race_member == 3) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
```{r}


```

