---
title: "October 26 report"
author: "Mireia Triguero"
date: "10/26/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment=NA, warning=FALSE, message=FALSE)
library(wesanderson)
library(tidyverse)
library(xtable)
library(stargazer)
setwd("~/Desktop/Sociology/RA/Data")
staff_salaries <- read_csv("staff_salaries_full.csv") %>%
  mutate(race_member2 = case_when(race_member == 0 ~ "White",
                                  race_member == 1 ~ "Black",
                                  race_member == 2 ~ "Hispanic",
                                  race_member == 3 ~ "Asian",
                                  TRUE ~ NA_character_))
options(qwraps2_markup = "markdown")
race_staffer <- read_csv("race_staffer.csv") %>% dplyr::select(-X1)

multiply100 <- function(x){
  x1 <- x*100
  return(x1)
}

```

## Overall ranking for Congress 

```{r}
staff_salaries %>% filter(office_type_id =="HM" | office_type_id =="SM") %>%
  filter(!is.na(rank)) %>%
  distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```
## Overall ranking for House
```{r}
staff_salaries %>% filter(office_type_id =="HM") %>%
  filter(!is.na(rank)) %>%
  distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```

## Overall ranking for Senate

```{r}
staff_salaries %>% filter(office_type_id =="SM") %>%
  filter(!is.na(rank)) %>%
  distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
# Rankings by Race of Lawmakers (house, senate, congress)


## House: White

```{r}

staff_salaries %>% filter(office_type_id =="HM" & race_member == 0) %>%
  distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```
## House: Black 

```{r}

staff_salaries %>% filter(office_type_id =="HM" & race_member == 1) %>%
  distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```
## House: Hispanic 

```{r}

staff_salaries %>% filter(office_type_id =="HM"  & race_member == 2) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## House: Asian 

```{r}

staff_salaries %>% filter(office_type_id =="HM" & race_member == 3) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## Senate: White 

```{r}

staff_salaries %>% filter(office_type_id =="SM" & race_member == 0) %>%
filter(!is.na(rank)) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```
## Senate: Black 

```{r}

staff_salaries %>% filter(office_type_id =="SM" & race_member == 1) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## Senate: Hispanic 

```{r}

staff_salaries %>% filter(office_type_id =="SM"  & race_member == 2) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## Senate: Asian

```{r}

staff_salaries %>% filter(office_type_id =="SM" & race_member == 3) %>% 
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## Congress: White 

```{r}

staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
  filter(!is.na(rank)) %>%
filter(race_member == 0) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)


```
## Congress: Black 

```{r}

staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
filter(race_member == 1) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## Congress: Hispanic 

```{r}

staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
filter(race_member == 2) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## Congress: Asian

```{r}

staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
filter(race_member == 3) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

# Rankings by political party (House, Senate, Congress)
## House: Republicans

```{r}

staff_salaries %>% filter(office_type_id == "HM") %>%
filter(party_id == 1) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## House: Democrats

```{r}

staff_salaries %>% filter(office_type_id == "HM") %>%
filter(party_id == 2) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## Senate: Republicans

```{r}

staff_salaries %>% filter(office_type_id =="SM") %>%
filter(!is.na(rank)) %>%
filter(party_id == 1) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## Senate: Democrats

```{r}

staff_salaries %>% filter(office_type_id =="SM") %>%
filter(party_id == 2) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```
## Congress: Republicans

```{r}

staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
filter(!is.na(rank)) %>%
filter(party_id == 1) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

## Congress: Democrats

```{r}

staff_salaries %>% filter(office_type_id =="SM" | office_type_id == "HM") %>%
filter(party_id == 2) %>%
    distinct(member_id, core_person_id, rank, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1)

```

#Promotion and Mobility
```{r}

staffers_2000 <- staff_salaries %>% 
  filter(year==2001) %>% 
  dplyr::select(core_person_id) %>% 
  distinct()

staff_lean <- staff_salaries %>% filter(!core_person_id %in% staffers_2000$core_person_id) %>% 
  group_by(core_person_id) %>% 
  arrange(year, core_person_id) %>%
  mutate(hill_experience = 1:n()) %>%
  ungroup() %>%
  group_by(core_person_id, member_office_id) %>%
  mutate(totdays = sum(total_days),
         democrat = ifelse(party_id == 2, 1, 0),
         republican = ifelse(party_id == 1, 1, 0))
staff_ed <- staff_lean %>% filter(degreeinfo == 1)

```

## Revisited estimates for how long staffers work on the Hill and the number of offices they are employed in calculated in discrete racial assignments

This is looking only at staffers that work directly for congressmember's offices (not committees, etc.)

```{r}
staff_salaries %>% group_by(race) %>%
  summarise(total_days = mean(total_days, rm.na=T))

# summary(lm(total_days ~ race, data = staff_salaries))

```




## Including an interaction between race and gender for compensation differences
## house salaries with interaction:
Models 1-2 are linear models with year fixed effects, models 3-4 are linear models with year and member fixed effecs. 

In the House, there seems to be a gendered and racialized difference. While Hispanic, white and Asian men get paid more on average, black man seem get paid less than black women. 

```{r}

library(lfe)

fit_house <- felm(salary_adj ~   black + hispanic + asian + gender + rank
                  + totdays + hill_experience + democrat + race_member2 + gender_member 
                 | year, 
                 data = subset(staff_lean, office_type_id == "HM"))

fit_house_interaction <- felm(salary_adj ~   (black + hispanic + asian) * gender + rank
                  + totdays + hill_experience + democrat + race_member2 + gender_member 
                 | year, 
                 data = subset(staff_lean, office_type_id == "HM"))

fit_senate <- felm(salary_adj ~  black + hispanic + asian + gender + rank
                 + totdays + hill_experience + democrat + race_member2 
                 + gender_member | year, 
                 data = subset(staff_lean, office_type_id == "SM"))

fit_senate_interaction <- felm(salary_adj ~  (black + hispanic + asian) * gender + rank
                 + totdays + hill_experience + democrat + race_member2 
                 + gender_member | year, 
                 data = subset(staff_lean, office_type_id == "SM"))

#stargazer(fit_house2, fit_senate2, type="text")

fit_house_fe <- felm(salary_adj ~ black + hispanic + asian + gender + rank
                  + totdays + hill_experience | member_office_id + year, 
                 data = subset(staff_lean, office_type_id == "HM"))

fit_house_fe_interaction <- felm(salary_adj ~   (black + hispanic + asian) * gender + rank
                  + totdays + hill_experience | member_office_id + year, 
                 data = subset(staff_lean, office_type_id == "HM"))

fit_senate_fe <- felm(salary_adj ~  black + hispanic + asian + gender + rank
                   + totdays + hill_experience | member_office_id + year, 
                  data = subset(staff_lean, office_type_id == "SM"))

fit_senate_fe_interaction <- felm(salary_adj ~   (black + hispanic + asian) * gender + rank
                   + totdays + hill_experience | member_office_id + year, 
                  data = subset(staff_lean, office_type_id == "SM"))

#stargazer(fit_house_fe, fit_senate_fe, type="text")

stargazer(title = "Compensation differences for the House (including interactions)", 
          fit_house, fit_house_interaction, fit_house_fe, fit_house_fe_interaction,
          type="text", 
          dep.var.labels = "Annual salary (in 2013 dollars)",
          no.space = T,
          column.sep.width="-12pt",
          digits = 0)

```

In the Senate, the race*gender interaction only seems to be different for Asian men (compared to women) (there is still an overall gender effect, where men get paid more, and race ffect (where non-white groups get paid less), but it's not signficantly different across racial groups)
```{r}

stargazer(title = "Compensation differences for the Senate (including interactions)", 
          fit_senate, fit_senate_interaction, fit_senate_fe, fit_senate_fe_interaction, type="text", 
          dep.var.labels = "Annual salary (in 2013 dollars)",
          column.sep.width="-12pt",
          no.space = T,
          digits = 0)
```


## Racial Composition of House, Senate, and Congress Staff


```{r}
# house <- staff_salaries %>% filter(office_type_id =="HM") %>% 
#   distinct(core_person_id, .keep_all = TRUE) %>%
#   group_by(race) %>% 
#   summarise(n = n()) %>%
#   ungroup() %>%
#   mutate(percentage = round(n/sum(n)*100, 1)) %>%
#   dplyr::select(percentage)
# 
# senate <- staff_salaries %>% filter(office_type_id =="SM") %>% 
#   distinct(core_person_id, .keep_all = TRUE) %>%
#   group_by(race) %>% 
#   summarise(n = n()) %>%
#   ungroup() %>%
#   mutate(percentage = round(n/sum(n)*100, 1))
# 
# prop.test(as.vector(house), as.vector(senate))


```

```{r}

p1 <- staff_salaries %>% filter(office_type_id == "HM" | office_type_id == "SM") %>%
  filter(year < 2013) %>%
  distinct (member_office_id, core_person_id, year, .keep_all = TRUE) %>%
  group_by(year, office_type_id) %>% 
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1) %>%
  pivot_longer(-c(year, office_type_id), names_to = "race", values_to = "pct")

p2 <- staff_salaries %>% filter(office_type_id == "HM" | office_type_id == "SM") %>%
  filter(year < 2013) %>%
  distinct (member_office_id, core_person_id, year, .keep_all = TRUE) %>%
  group_by(year) %>% 
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_at(c("black", "white", "asian", "hispanic"), multiply100) %>%
  mutate_if(is.numeric, round, 1) %>%
  pivot_longer(-year, names_to = "race", values_to = "pct") %>%
  mutate(office_type_id = "Congress")
p3 <- bind_rows(p1,p2)  
  
p3 %>%  ggplot(aes(x = year, y = pct, color = office_type_id)) +
  geom_smooth()+
  facet_wrap(~race, scales = "free_y") +
  scale_x_continuous(breaks = seq(2000, 2012, 2)) +
  scale_color_manual(values=wes_palette(n=4, name="GrandBudapest1"))


```
## What percentage of all Black Staff work for Black members? (etc.) to answer comment on page 5 of draft 4

```{r}

staff_salaries %>% 
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  mutate(white_member = ifelse(race_member == 0, 1, 0),
         black_member = ifelse(race_member == 1, 1, 0),
         hispanic_member = ifelse(race_member == 2, 1, 0),
         asian_member = ifelse(race_member == 3, 1,0)) %>%
  group_by(race) %>%
  summarise_at(c("black_member", "white_member", "asian_member", "hispanic_member"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 


```

## Comparison of white/non-white members offices for Congress, Senate and House. 
### House:
```{r}
staff_salaries %>% filter(office_type_id =="HM") %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  mutate(white_nonwhite = ifelse(race_member == 0, "white", "non_white")) %>%
  group_by(white_nonwhite) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 

```
### Senate:
```{r}
staff_salaries %>% filter(office_type_id =="SM") %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  mutate(white_nonwhite = ifelse(race_member == 0, "white", "non_white")) %>%
  group_by(white_nonwhite) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 

```

```{r}
staff_salaries %>% 
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  group_by(rank) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), count) 

```

### Congress:
```{r}
staff_salaries %>%
  distinct(member_id, core_person_id, .keep_all = TRUE) %>%
  mutate(white_nonwhite = ifelse(race_member == 0, "white", "non_white")) %>%
  group_by(white_nonwhite) %>%
  summarise_at(c("black", "white", "asian", "hispanic"), mean) %>%
  mutate_if(is.numeric, multiply100) %>%
  mutate_if(is.numeric, round, 1) 

```
